RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-07-27 review/response.tex

\begin{letter}{%
		Guest Editors\\
		IEEE Journal on Selected Areas in Communications
	}
	\opening{Dear Editors and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of ``RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface''.
	We would like to express our sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below, we prepare a point-to-point response and describe all the changes made to the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of JSAC publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	Although the paper presents a novel idea and tackles an interesting problem, it requires great effort to improve the presentation, the language, and the mathematical derivations. Detailed comments are given as follows:

	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
	\reply {We apologize for the mistake. The abstract and the number of keywords have been revised to meet the specifications.}

	\point The manuscript contains multiple grammatical errors and unclear sentences that require correction. Please revise the manuscript for improved clarity. For instance, in the first paragraph of Section II, Subsection B, the sentence "It is assumed that the signal reflected by two or more times is negligible" is not clear.
	\reply {We have thoroughly revised the manuscript to address the grammatical errors and improve sentence clarity. The example sentence has been revised to ``It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.''}

	\point Please consider defining all acronyms (e.g., MRC) and all the notations in Section I (e.g., the mutual information, probabilities, etc.,).
	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper. We tried to add a list of acronyms and notations, but it would violate the 30-page limit and we cannot squeeze enough space from other places. Therefore, we decided not to include the list. We have ensured that all acronyms are defined before their first usage.}
